Two Problems for Sophistication

### 2015-01-21 Facticity/Facticity/paper.tex
plaatjes in intro

\usepackage{amsmath,amsfonts}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[mathscr]{eucal}
\usepackage{thmtools}

@@

For any string $x$, there may be many different two-part representations. The total code length can never be less than the Kolmogorov complexity, but it can come close. The balance between the two parts may vary; Figure~\ref{fig:todo} provides an illustration. The various proposals then define sophistication in terms of the length of the structure part of this two-part code for one of the representations that (almost) achieves the Kolmogorov complexity. However, For most of these definitions, we can prove that they fail one or more of the conditions above. Vit\'anyi's definition \cite{vitanyi2004meaningful} is the one exception that we cannot \emph{prove} to conflict with our requirements, but we can show that only strings that require an enormous amount of processing to construct, yield a large sophistication.

>>>>

\usepackage{amsmath,amsfonts}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage[mathscr]{eucal}
\usepackage{thmtools}
\usepackage{graphicx}
\usepackage{caption}

@@

\begin{figure*}[tb]
  \hspace{-2.8em}
  \begin{minipage}{0.55\textwidth}
     \includegraphics[width=\textwidth]{./img/sophistication.pdf}
  \end{minipage}
  \begin{minipage}{0.55\textwidth}
     \includegraphics[width=\textwidth]{./img/sophistication-jump.pdf}
  \end{minipage}
  \caption{\small (left) Two-part representations of $x$. The horizontal axis measures the bits used to describe the model, the vertical axis measures the number of bits used to describe the noise. The smallest possible effective description, denoted by a black diagonal, is $C^\M(x)$. We accept all representations that are close to this optimum, the threshold being represented by a dashed line. The size of the smallest model within the slack is the sophistication of the data. (right) The same image, after a constant perturbation in te model complexity caused by a change in numbering.}
  \label{fig:diagram}
\end{figure*}

For any string $x$, there may be many different two-part representations. The total code length can never be less than the Kolmogorov complexity, but it can come close. The balance between the two parts may vary; Figure~\ref{fig:diagram} provides an illustration. The various proposals then define sophistication in terms of the length of the structure part of this two-part code for one of the representations that (almost) achieves the Kolmogorov complexity. However, For most of these definitions, we can prove that they fail one or more of the conditions above. Vit\'anyi's definition \cite{vitanyi2004meaningful} is the one exception that we cannot \emph{prove} to conflict with our requirements, but we can show that only strings that require an enormous amount of processing to construct, yield a large sophistication.
